Reflections from reproductions

### 2024-08-19 pages/reflections.qmd
docs(reflections): finished page (exc. johnson which not done yet)

* Reduce model run time if possible as it makes it easier to work with, and facilitates doing full re-runs of all scenarios (which can be important with code changes, etc).
* Common issue (to varying degrees - i.e. taking 20 minutes, up to taking several hours).

@@

* At least provide a script that can run the baseline model as in the paper (even if not providing the scenarios)

@@

@huang_optimizing_2019: In this case, patient arrivals and resource numbers were listed in the paper, and there were several discprepancies between this and the provided code. However, for many of the model parameters like length of appointment, these were not mentioned in the paper, and so it was not possible to confirm whether or not those were correct.

@lim_staff_2020: For Figure 5, had to guess the value for `staff_per_shift`.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | <!--TODO--> | ✅ | <!--TODO--> | N/A |

@shoaib_simulation_2021: Although there was a scenario table, this did not include all the parameters I would need to change. It was more challenging to identify parameters that were only described in the body of the article. There were also some discrepancies in parameters between the main text of the article, and the tables and figures. Some scenarios were quite ambiguous/unclear from their description in the text, and I initially misunderstood the required parameters for the scenarios.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | <!--TODO--> | <!--TODO--> | N/A |

@shoaib_simulation_2021: It was unclear how to estimate inter-arrival time

@huang_optimizing_2019: The calculations for inter-arrival times were provided in the code, and the inputs to the code were the number of arrivals, as reported in the paper, and so making it easy to compare those parameters and check if numbers were correct or not.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | <!--TODO--> | ❌ | <!--TODO--> | ✅ |

@anagnostou_facs-charm_2022: Outputs to `OUT_STATS.csv`.

@@

E.g. Easy to figure out how to use output table/s to create tables/figures.

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | <!--TODO--> | <!--TODO--> | <!--TODO--> | ✅ |

For @shoaib_simulation_2021, there were two alternative results spreadsheets with some duplicate metrics but sometimes differing results between them, which made it a bit confusing to work out what to use.

@anagnostou_facs-charm_2022: The layout of the results spreadsheet was simple, understandable and easy to read, making it easy to adapt into figures.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ✅ | ✅ |

@shoaib_simulation_2021: The lack of seeds wasn't actually a barrier to the reproduction though due to the replication number. I later add seeds so my results could be reproduced, and found that the ease of setting seeds with salabim was a greater facilitator to the work. I only had to change one or two lines of code to then get consistent results between runs (unlike other simulation software like SimPy where you have to consider the use of seeds by different sampling functions). Moreover, by default, salabim would have set a seed (although overridden by original authors to enable them to run replications).

@huang_optimizing_2019: It would have been beneficial to include seeds, as there was a fair amount of variability, so with seeds I could then I could be sure that my results do not differ from the original simply due to randomness.

@lim_staff_2020: The results obtained looked very similar to the original article, with minimal differences that I felt to be within the expected variation from the model stochasticity. However, if seeds had been present, we would have been able to say with certainty. I did not feel I needed to add seeds during the reproduction to get the same results.

@anagnostou_facs-charm_2022: The authors included a random seed so the results I got were identical to the original (so no need for any subjectivity in deciding whether its similar enough, as I could perfectly reproduce).

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | N/A | <!--TODO--> | ❌ |

@@

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ❌ | ❌ |

@huang_optimizing_2019: Had to write code from scratch. For one of the figures, it would have been handy if informed that plot was produced by a simmer function (as didn’t initially realise this). It also took a bit of time for me to work out how to transform the figure axes as this was not mentioned in the paper (and no code was provided for these). It was also unclear and a bit tricky to work out how to standardise the density in the figures (since it is only described in the text and no formula/calculations are provided there or in the code). <!-- TODO: Consider whether this should be split into another box (i.e. about providing the processing?) -->

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | N/A |

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| <!--TODO--> | <!--TODO--> | <!--TODO--> | <!--TODO--> | ✅ |

@anagnostou_facs-charm_2022: Clear README with instructions on how to run the model was really helpful.

@@

For @lim_staff_2020, the simplicity of the model structure and code, and simplicity and similarity between figures, really helped to facilitate the reproduction. For @kim_modelling_2021, reproduction was facilitated by having relatively simple and repetitive plots which were easy to understand and create. For @anagnostou_facs-charm_2022, the figures were simple (just means and CI which are already calculated).

Fix errors in script. For @kim_modelling_2021, an error appears to have been introduced with the aoorta diameter thresholds by switching between nested and unnested lists, which I’m anticipating was unresolved due to the long run times of the model meaning they weren’t all run in sequence at the end. <!--TODO: Have put in run time, or does it need seperate place -->

@anagnostou_facs-charm_2022: Although not needed for the reproduction itself, when I tried to amend the name and location of the csv file output the model for use in tests, this was very tricky to do as it was hard coded into the scripts and I found difficult to amend due to how the model is run and set up. <!-- TODO: Fall under hard coding? Or output file flexibility? -->

@@

<!-- TODO: Check if any of these should be above. e.g. might want to put simplicity in a same way as i put run time - as simplicity is not inherently required (its about focus of project partly) BUT it is really handy (and it is always a good principle to hold) -->

>>>>

* Reduce model run time if possible as it makes it easier to work with, and facilitates doing full re-runs of all scenarios (which can be important with code changes, etc).
    * Relatedly, it is good practice to re-run all scripts before finishing up, as then you can spot any errors like the one mentioned for @kim_modelling_2021
* Common issue (to varying degrees - i.e. taking 20 minutes, up to taking several hours).

@@

* At least provide a script that can run the baseline model as in the paper (even if not providing the scenarios)
* This can introduce difficulties - when some parameters are wrong, you rely on the paper to check which parameters are correct or not, but if the paper doesn't mention every single parameter (which is reasonably likely, as this includes those not varied by scenarios), then you aren't able to be sure that the model you are running is correct.

@@

@huang_optimizing_2019: Not met. In this case, patient arrivals and resource numbers were listed in the paper, and there were several discprepancies between this and the provided code. However, for many of the model parameters like length of appointment, these were not mentioned in the paper, and so it was not possible to confirm whether or not those were correct. Hence, marked as not met, as the presence of discrepenancies for several other parameters puts these into doubt.

@lim_staff_2020: Not met. For Figure 5, had to guess the value for `staff_per_shift`.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | 🟡 | N/A | N/A | <!--TODO--> |

@shoaib_simulation_2021: Not met. Although there was a scenario table, this did not include all the parameters I would need to change. It was more challenging to identify parameters that were only described in the body of the article. There were also some discrepancies in parameters between the main text of the article, and the tables and figures. Some scenarios were quite ambiguous/unclear from their description in the text, and I initially misunderstood the required parameters for the scenarios.

@huang_optimizing_2019: Not met. As described above, paper didn't adequately describe all parameters.

@lim_staff_2020: Partially met. Nearly all parameters are in the paper table, and others are described in the article. However, didn't provide information for the `staff_per_shift` for Figure 5.

@kim_modelling_2021 and @anagnostou_facs-charm_2022: Not applicable. All provided.

* Provide parameters in a table (including for each scenario), as it can be difficult/ambiguous to interpret them from the text, and hard to spot them too.
* Be sure to mention every parameter that gets changed (e.g. for @lim_staff_2020, as there wasn't a default `staff_per_shift` across all scenarios, but not stated for the scenario, had to guess it).

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ✅ | N/A | N/A | N/A | <!--TODO--> |

@shoaib_simulation_2021: Not met. It was unclear how to estimate inter-arrival time.

@huang_optimizing_2019: Fully met. The calculations for inter-arrival times were provided in the code, and the inputs to the code were the number of arrivals, as reported in the paper, and so making it easy to compare those parameters and check if numbers were correct or not.

@lim_staff_2020: Not applicable. The parameter not provided is not one that you would calculate.

@kim_modelling_2021 and @anagnostou_facs-charm_2022: Not applicable. All provided.

* If you are going to be mentioning the "pre-processed" values at all, then its important to include the calculation (ideally in the code, as that is the clearest demonstration of exactly what you did)

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ✅ | ❌ | ❌ | ❌ | ✅ | <!--TODO--> |

@shoaib_simulation_2021: Fully met. Outputs to `.xlsx` files

@huang_optimizing_2019, @lim_staff_2020, and @kim_modelling_2021: Not met. Outputs to dataframe/s.

@anagnostou_facs-charm_2022: Outputs to `OUT_STATS.csv`. Note: Although not needed for the reproduction itself, when I tried to amend the name and location of the csv file output the model for use in tests, this was very tricky to do as it was hard coded into the scripts and I found difficult to amend due to how the model is run and set up.

* Common issue
* Particularly important if model run time is even slightly long (even just minutes long, but even more so as becomes many minutes / hours), so don't always have to re-run it each time to get results
* Set up this in such a way that it is easy to change the name and location of the output file.

@@

@shoaib_simulation_2021: Not met. There were two alternative results spreadsheets with some duplicate metrics but sometimes differing results between them, which made it a bit confusing to work out what to use.

@huang_optimizing_2019, @lim_staff_2020, and @anagnostou_facs-charm_2022: Fully met. Didn't experience issues interpreting the contents of the output table/s.

@kim_modelling_2021: Not met. It took me a little while to work out what surgery columns I needed, and to realise I needed to combine two of them. This required looking at what inputs genreated this, and referring to a input data dictionary.

* Don't provide alternative results for the same metrics
* Make it clear what each colum/category in the results table means, if it might not be immediately clear.

@@

@shoaib_simulation_2021: Not met. The lack of seeds wasn't actually a barrier to the reproduction though due to the replication number. I later add seeds so my results could be reproduced, and found that the ease of setting seeds with salabim was a greater facilitator to the work. I only had to change one or two lines of code to then get consistent results between runs (unlike other simulation software like SimPy where you have to consider the use of seeds by different sampling functions). Moreover, by default, salabim would have set a seed (although overridden by original authors to enable them to run replications).

@huang_optimizing_2019: Not met. It would have been beneficial to include seeds, as there was a fair amount of variability, so with seeds I could then I could be sure that my results do not differ from the original simply due to randomness.

@lim_staff_2020: Not met. The results obtained looked very similar to the original article, with minimal differences that I felt to be within the expected variation from the model stochasticity. However, if seeds had been present, we would have been able to say with certainty. I did not feel I needed to add seeds during the reproduction to get the same results.

@kim_modelling_2021: Fully met. Included a seed, although I don't get identical results as I had to reduce number of people in simulation.

@anagnostou_facs-charm_2022: Fully met. The authors included a random seed so the results I got were identical to the original (so no need for any subjectivity in deciding whether its similar enough, as I could perfectly reproduce).

* Depending on your model and the outputs/type of output you are looking at, the lack of seeds can have varying impacts on the appearance of your results, and can make the subjective judgement of whether results are consistent harder (if discrepancies could be attributed to not having consistent seeds or not).
* It can be really quite simple to include seeds.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | N/A | 🟡 | ❌ | N/A | <!--TODO--> |

@@

@shoaib_simulation_2021: Not met.

@huang_optimizing_2019: Not applicable. No tables in scope.

@lim_staff_2020: Partially met. It outputs the results in a similar structure to the paper (like a section of a table). However, it doesn't have the full code to produce a table outright, for any of the tables, so additional processing still required.

@kim_modelling_2021: Not met. Had to write code to generate tables, which included correctly implementing calculation of excess e.g. deaths, scaling to population size, and identify which columns provide the operation outcomes.

@anagnostou_facs-charm_2022: Not applicable. No tables in scope.

* It can take a bit of time to do this processing, so very handy for it to be provided.
* Common issue.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | ❌ | ❌ | <!--TODO--> |

@shoaib_simulation_2021: Not met.

@huang_optimizing_2019: Not met. Had to write code from scratch. For one of the figures, it would have been handy if informed that plot was produced by a simmer function (as didn’t initially realise this). It also took a bit of time for me to work out how to transform the figure axes as this was not mentioned in the paper (and no code was provided for these). It was also unclear and a bit tricky to work out how to standardise the density in the figures (since it is only described in the text and no formula/calculations are provided there or in the code). <!-- TODO: Consider whether this should be split into another box (i.e. about providing the processing?) -->

@lim_staff_2020, @kim_modelling_2021 and @anagnostou_facs-charm_2022: Not met. However, the simplicity and repetition of the figures was handy.

* It can take a bit of time to do this processing, particularly if the figure involves any transformations (and less so if the figure is simple), so very handy for it to be provided.
* Common issue.

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | N/A | ❌ | N/A | <!--TODO--> |

@shoaib_simulation_2021, @huang_optimizing_2019, @kim_modelling_2021: Not met.

@lim_staff_2020, @anagnostou_facs-charm_2022: Not applicable (no in-text results).

* Provide code to calculate in-text results
* Common issue

@@

| @shoaib_simulation_2021 | @huang_optimizing_2019 | @lim_staff_2020 | @kim_modelling_2021 | @anagnostou_facs-charm_2022 | @johnson_cost_2021 |
| :-: | :-: | :-: | :-: | :-: | :-: |
| ❌ | ❌ | ❌ | 🟡 | ✅ | <!--TODO--> |

@shoaib_simulation_2021: Not met. No instructions, although is just a single script that you run.

@huang_optimizing_2019: Not met. Not provided in runnable form but, regardless, no instructions for running it as it is provided (as a web application - i.e. no info on how to get that running).

@lim_staff_2020: Not met. No instructions, although is just a single script that you run.

@kim_modelling_2021: Partially met. README tells you which folder has the scripts you need, although nothing further. Although all you need to do is run them.

@anagnostou_facs-charm_2022: Fully met. Clear README with instructions on how to run the model was really helpful.

* Even if as simple as running a script, include instructions on how to do so
* Common issue

@@

@@

* Include grid lines
* Include data dictionaries
